\documentclass{article}
\input{preamble/preamble}
\input{preamble/preamble_acronyms}
\input{preamble/preamble_math}
\input{preamble/preamble_tikz}

\title{
Edward: A library for probabilistic modeling,\break inference, and criticism
}

\author{
Dustin Tran, Alp Kucukelbir, Adji B.~Dieng,\\
Maja Rudolph, Dawen Liang, and David M.~Blei\\\\
Columbia University
}

\begin{document}

\hypersetup{pageanchor=false}
\begin{titlepage}
\maketitle
\begin{abstract}
  Probabilistic modeling is a powerful approach for analyzing
  empirical information.
  We describe \emph{Edward}, a library for probabilistic modeling.
  Edward's design reflects an iterative process pioneered by George
  Box: build a model of a phenomenon, make inferences about the model given
  data, and criticize the model's fit to the data. Edward supports a broad class
  of probabilistic models, efficient algorithms for inference, and many
  techniques for model criticism. The library builds on top of
  TensorFlow to support distributed training and hardware such as
  GPUs.
  Edward enables the development of complex probabilistic
  models and their algorithms at a massive scale.
\end{abstract}

\emph{Keywords:}
Probabilistic Models;
Bayesian Inference;
Model Criticism;
Neural Networks;
Scalable Computation;
Probabilistic Programming.%
\footnote{Details in this paper describe Edward version 1.2.1,
released Jan 30, 2017.}

\setcounter{secnumdepth}{2}
\setcounter{tocdepth}{2}
\tableofcontents

\thispagestyle{empty}
\end{titlepage}
\hypersetup{pageanchor=true}

\glsresetall{}

\clearpage

\input{intro}
\input{related}
\clearpage
\input{getting_started}
\clearpage
\input{design}
\input{data}
\input{model}
\input{model_compositionality}
\input{model_development}
\input{inference}
\input{inference_classes}
\input{inference_compositionality}
\input{inference_data_subsampling}
\input{inference_development}
\input{criticism}
\input{criticism_point_evaluation}
\input{criticism_ppc}
\clearpage
\input{examples}

\clearpage
\section{Acknowledgments}
Edward has benefited enormously from the helpful feedback and advice
of many individuals: Jaan Altosaar, Eugene Brevdo, Allison Chaney,
Joshua Dillon, Matthew Hoffman, Kevin Murphy, Rajesh Ranganath, Rif
Saurous, and other members of the Blei Lab, Google Brain, and Google
Research.
This work is supported by NSF IIS-1247664, ONR N00014-11-1-0651,
DARPA FA8750-14-2-0009, DARPA N66001-15-C-4032, Adobe, Google, NSERC
PGS-D, and the Sloan Foundation.

\clearpage
\bibliographystyle{apalike}
\bibliography{bib}

\end{document}
